Model-based variable selection for regression with highly correlated variables.

### 2014-08-22 www/article.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@815 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

However, $\mathcal{S}$ being combinatorial, $|\mathcal{S}|$ is huge. It has two cumulated consequences: First, the {\it exact} probability $\mathbb{P}(\boldsymbol{S}|\boldsymbol{X})$ may be of the same order of magnitude for a large number of candidates  $\boldsymbol{S}$, including the best one; Second, the {\sc bic} {\it approximations} of this quantity may introduce additional confusion to wisely distinguish between model probabilities. In order to limit this problem, we propose to introduce some information in $\mathbb{P}(\boldsymbol{S})$ promoting simple models through the following {\it hierarchical} uniform distribution denoted by $\mathbb{P}_H(\boldsymbol{S})$:
\begin{eqnarray}
\mathbb{P}_H(\boldsymbol{S}) & = & \mathbb{P}_H(\boldsymbol{J}_r,\boldsymbol{J}_p) \\
 & = & \mathbb{P}_H(\boldsymbol{J}_r,\boldsymbol{J}_p,d_r,\boldsymbol{d}_p) \\
 & = & \mathbb{P}_U(\boldsymbol{J}_p|\boldsymbol{d}_p,\boldsymbol{J}_r,d_r) \times \mathbb{P}_U(\boldsymbol{d}_p|\boldsymbol{J}_r,d_r) \times \mathbb{P}_U(\boldsymbol{J}_r|d_r)\times \mathbb{P}_U(d_r) \\
 & = & \left[\prod_{j=1}^{d_r} \left(\begin{array}{c} d-d_r \\ d_p^j \end{array}\right) \right]^{-1} \times \left[d-d_r\right]^{-d_r} \times \left[\left(\begin{array}{c} d \\ d_r \end{array} \right)\right]^{-1} \times [d+1]^{-1},
\end{eqnarray}
where $\left(\begin{array}{c} a \\ b \end{array}\right)$ designs the number of b-element subsets of an a-element set and where all probabilities $\mathbb{P}_U(\cdot)$ denote uniform distribution on the related space at hand. $\mathbb{P}_H(\boldsymbol{S})$ gives decreasing probabilities to more complex models, provided that the following new hypothesis is verified:

>>>>

However, $\mathcal{S}$ being combinatorial, $|\mathcal{S}|$ is huge. It has two cumulated consequences: First, the {\it exact} probability $\mathbb{P}(\boldsymbol{S}|\boldsymbol{X})$ may be of the same order of magnitude for a large number of candidates  $\boldsymbol{S}$, including the best one; Second, the {\sc bic} {\it approximations} of this quantity may introduce additional confusion to wisely distinguish between model probabilities. In order to limit this problem, we propose to introduce some information in $\mathbb{P}(\boldsymbol{S})$ promoting simple models through the following {\it hierarchical} uniform distribution denoted by $\mathbb{P}_H(\boldsymbol{S})$:
\begin{eqnarray}
\mathbb{P}_H(\boldsymbol{S}) & = & \mathbb{P}_H(\boldsymbol{J}_r,\boldsymbol{J}_p) \\
 & = & \mathbb{P}_H(\boldsymbol{J}_r,\boldsymbol{J}_p,d_r,\boldsymbol{d}_p) \\
 & = & \mathbb{P}_U(\boldsymbol{J}_p|\boldsymbol{d}_p,\boldsymbol{J}_r,d_r) \times \mathbb{P}_U(\boldsymbol{d}_p|\boldsymbol{J}_r,d_r) \times \mathbb{P}_U(\boldsymbol{J}_r|d_r)\times \mathbb{P}_U(d_r) \\
 & = & \left[\prod_{j=1}^{d_r} \left(\begin{array}{c} d-d_r \\ d_p^j \end{array}\right) \right]^{-1} \times \left[d-d_r\right]^{-d_r} \times \left[\left(\begin{array}{c} d \\ d_r \end{array} \right)\right]^{-1} \times [d+1]^{-1},
\end{eqnarray}
where $\left(\begin{array}{c} a \\ b \end{array}\right)$ means the number of b-element subsets of an a-element set and where all probabilities $\mathbb{P}_U(\cdot)$ denote uniform distribution on the related space at hand. $\mathbb{P}_H(\boldsymbol{S})$ gives decreasing probabilities to more complex models, provided that the following new hypothesis is verified:
